Abstract Data Type Inference

### 2015-03-07 inference.tex
Interpretation of history formulas.

An \emph{implementation} $\mathcal{I}$ is a labeled transition system whose
traces are executions. The histories $H(\mathcal{I})$ of an implementation are
the histories of its traces. An \emph{abstract data type (ADT)} $A$ is the set
$H(\mathcal{I})$ of histories of \emph{some} implementation $\mathcal{I}$. We
define \emph{observational refinement} between two implementations, or between
an implementation and an ADT, as history-set inclusion. We say $\mathcal{I}_1$
\emph{refines} $\mathcal{I}_2$ if{f} $H(\mathcal{I}_1) \subseteq
H(\mathcal{I}_2)$, and $\mathcal{I}$ \emph{refines} $A$ if{f} $H(\mathcal{I})
\subseteq A$.

TODO DEFINE HISTORY LOGIC

The \emph{symbolic ADT inference problem} is to compute a first-order history
formula $F$ for a given ADT $A$ such that
\begin{itemize}

@@

\end{itemize}
where $B$ is the complement of $\ker A$.

>>>>

An \emph{implementation} $\mathcal{I}$ is a prefixed-closed set of executions.
An \emph{abstract data type (ADT)} $A$ is the set $H(\mathcal{I})$ of histories
of an implementation $\mathcal{I}$. We define \emph{observational refinement}
between two implementations, or between an implementation and an ADT, as
history-set inclusion. We say $\mathcal{I}_1$ \emph{refines} $\mathcal{I}_2$
if{f} $H(\mathcal{I}_1) \subseteq H(\mathcal{I}_2)$, and $\mathcal{I}$
\emph{refines} $A$ if{f} $H(\mathcal{I}) \subseteq A$.

In the following we fix a symbolic representation of ADTs on which to base our
symbolic ADT inference problem. A \emph{history formula} $F$ is a first-order
logic formula with
\begin{itemize}

  \item variables ranging over operation identifiers,

  \item constants from $\mathbb{M}$ for method names,

  \item a function symbol $\mathsf{m}$ for matching, and

  \item predicate symbols $\mathsf{c}$ and $\mathsf{<}$ for completion and
  order.

\end{itemize}
A history formula $F$ is interpreted over a history $h$ in the natural way, by
binding variables to the operations of $h$, and binding function and predicate
symbols to their interpretations in $h$. We write $h \models F$ when $h$ is a
model of $F$, and $h \not\models F$ otherwise.

  TODO HISTORY FORMULA EXAMPLE

TODO DEFINE KERNEL AND COMPLEMENT

A history formula $F$ \emph{represents} an ADT $A$ when:
\begin{itemize}

@@

\end{itemize}
where $B$ is the complement of $\ker A$. The \emph{symbolic ADT inference
problem} is to compute a history formula $F$ representing the ADT of a given
implementation $\mathcal{I}$.
